Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-20 content/example.tex
loc and classes to table
explanations; modifying table more

In the table, the number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. 
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.

\begin{table}
\caption{Frequencies of correlated-call occurrences in the Dacapo benchmarks}\label{tab:dacapostat}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrr
>{\columncolor[HTML]{FFFFFF}}r 
>{\columncolor[HTML]{FFFFFF}}l r@{}}
\toprule
\textbf{Benchmark}  &
  \multicolumn{1}{c}{\textbf{$|C|$}} & 
  \multicolumn{1}{c}{\textbf{$|C_P|$}} & 
  \multicolumn{1}{c}{\textbf{$|C^\Subset|$}} & 
  \multicolumn{1}{c}{\textbf{$|\rcc|$}} & 
  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C_P|}{|C|}$\end{tabular}}} & 
  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|C_P|}$\end{tabular}}} & 
  \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|\rcc|}$\end{tabular}} \\ \midrule
\textbf{antlr}      & 7,610                             & 428                                   & 299                              & 70                                   & {\textbf{6\%}}                                                      & {\textbf{70\%}}                                                     & 4                                                                \\
\textbf{bloat}      & 18,157                            & 933                                   & 429                              & 119                                  & {\textbf{5\%}}                                                      & {\textbf{46\%}}                                                     & 4                                                                \\
\textbf{chart}      & 18,101                            & 466                                   & 195                              & 61                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
\textbf{eclipse}    & 3,222                             & 100                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{35\%}}                                                     & 4                                                                \\
\textbf{fop}        & 4,831                             & 129                                   & 40                               & 12                                   & {\textbf{3\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
\textbf{hsqldb}     & 3,573                             & 81                                    & 35                               & 10                                   & {\textbf{2\%}}                                                      & {\textbf{43\%}}                                                     & 4                                                                \\
\textbf{jython}     & 12,149                            & 487                                   & 129                              & 54                                   & {\textbf{4\%}}                                                      & {\textbf{26\%}}                                                     & 2                                                                \\
\textbf{luindex}    & 7,190                             & 188                                   & 79                               & 29                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
\textbf{lusearch}   & 9,043                             & 350                                   & 126                              & 47                                   & {\textbf{4\%}}                                                      & {\textbf{36\%}}                                                     & 3                                                                \\
\textbf{pmd}        & 10,972                            & 219                                   & 68                               & 23                                   & {\textbf{2\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
\textbf{xalan}      & 3,889                             & 110                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{32\%}}                                                     & 4                                                                \\
\textbf{Geom. mean} & \textbf{7,572}                    & \textbf{240}                          & \textbf{91}                      & \textbf{29}                          & {\textbf{3\%}}                                                      & {\textbf{38\%}}                                                     & \textbf{3}                                                       \\ \bottomrule
\end{tabular}
%}
\end{table}

>>>>

In the table, the number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.

\input{tables/stats}
